Comparison of Catalogs

### 2024-07-19 compare/compare.qmd
if c=0 no plot + abs+lum

```{python}
def compare_data(x, y, unc = None):
    """
    Performs a linear comparison between two datasets.

@@

    Returns:
    tuple: A tuple containing the following elements:
        - slope (float): The slope of the fitted linear model.
        - intercept (float): The intercept of the fitted linear model.
        - r2 (float): The R-squared value, indicating the proportion of variance explained by the linear model.
        - corr (float): The Pearson correlation coefficient, measuring the linear correlation between x and y.
    """
    x_data = np.ma.array(x.value, mask=np.isnan(x.value))
    y_data =  np.ma.array(y.value, mask=np.isnan(y.value))
    if unc is None:
        w = None
    else:
        unc = np.ma.array(unc.value, mask=np.isnan(x.value))
        w = 1/unc 
    # initialize a linear fitter
    fit = fitting.LinearLSQFitter()

@@

    # fit the data with the fitter
    fitted_line = fit(line_init, x_data, y_data, weights = w)
    slope = fitted_line.slope.value
    intercept = fitted_line.intercept.value

@@

    return slope, intercept, r2, corr
```

@@

    # Plot the fitted line with unit support
    plt.plot(x, c*x + m*x.unit, c = "red", label = f"Fit: {y.info.name}$_H $= {c:.2f}$\cdot${x.info.name}$_L${m:+.2f}\n $R^2=$ {r2:.2f}")

@@

ttype_corr = round(compare_data(dt["TType"], dt["T"])[3], 4)
inc_corr = round(compare_data(dt["inc"], dt["I"])[3], 3)
#a26_corr = round(compare_data(dt["a26_1"], dt["R1"])[3], 3)
#it doesnt even compute
```

|      LCV      |        HECATE        |                        Description                        | Pearson Correlation \[-1,1\] |
|:---------------:|:---------------:|:-------------------:|:---------------:|
|     TType     |   T (with errors)    | Numerical Hubble type following the de Vaucouleurs system |    `{python} ttype_corr`     |
|      inc      |          I           |                     Inclination (deg)                     |     `{python} inc_corr`      |
| a26_1 (Major) | R1 (Semi-major axis) |                 angular diameter (arcmin)                 |              0               |

As we can see we don't have any significant correlation between the data

@@

dt["TType"].info, dt["T"].info
```

@@

|   LCV   | HECATE | Description |
|:-------:|:------:|:-----------:|
| logKLum | logL_K |             |
|         |        |             |
|         |        |             |

@@

|         LCV         | HECATE | Description |
|:-------------------:|:------:|:-----------:|
| mag_B (with errors) |        |             |
|       mag_FUV       |        |             |
|                     |        |             |

## Absorbsion

|  LCV   | HECATE |                  Description                   |
|:------:|:------:|:----------------------------------------------:|
|   AB   |   AG   |    Galactic extinction/absorption in B band    |
| AB_int |   AI   | Internal/Intrisic B band extinction/absorption |

## SFR

>>>>

```{python}
def compare_data(x, y, unc=None):
    """
    Performs a linear comparison between two datasets.

@@

    Returns:
    tuple: A tuple containing the following elements:
        - slope (float): The slope of the fitted linear model.
        - intercept (float): The intercept of the fitted linear model.
        - r2 (float): The R-squared value, indicating the proportion of variance explained by the linear model.
        - corr (float): The Pearson correlation coefficient, measuring the linear correlation between x and y.
    """
    try:
        x_data = np.ma.array(x.value, mask=np.isnan(x.value))
        y_data = np.ma.array(y.value, mask=np.isnan(y.value))
        if unc is None:
            w = None
        else:
            unc = np.ma.array(unc.value, mask=np.isnan(x.value))
            w = 1 / unc
        # initialize a linear fitter
        fit = fitting.LinearLSQFitter()

@@

        # fit the data with the fitter
        fitted_line = fit(line_init, x_data, y_data, weights=w)
        slope = fitted_line.slope.value
        intercept = fitted_line.intercept.value

@@

        return slope, intercept, r2, corr
    except Exception:
        return 0, 0, 0, 0
```

@@

    # Plot the fitted line with unit support
    if c!=0:
        plt.plot(x, c*x.value+ m, c = "red", label = f"Fit: {y.info.name}$_H $= {c:.2f}$\cdot${x.info.name}$_L${m:+.2f}\n $R^2=$ {r2:.2f}")

@@

ttype_corr = round(compare_data(dt["TType"], dt["T"])[3], 4)
inc_corr = round(compare_data(dt["inc"], dt["INCL"])[3], 3)
a26_corr = round(compare_data(dt["a26_1"], dt["A26_1a"])[3], 3)
```

|      LCV      |        HECATE        |                        Description                        | Pearson Correlation \[-1,1\] |
|:---------------:|:---------------:|:-------------------:|:---------------:|
|     TType     |   T (with errors)    | Numerical Hubble type following the de Vaucouleurs system |    `{python} ttype_corr`     |
|      inc      |          INCL           |                     Inclination (deg)                     |     `{python} inc_corr`      |
| a26_1 (Major) | A26_1a (Semi-major axis) |                 angular diameter (arcmin)                 |              `{python} a26_corr`               |

As we can see we don't have any significant correlation between the Types of galaxies

@@

scatter_plot(dt["TType"], dt["T"], yerr = dt["E_T"])
scatter_plot(dt["inc"], dt["INCL"], yerr = dt["E_V"])
scatter_plot(dt["a26_1"], dt["A26_1a"], yerr = dt["E_V"])

```

**For the A26: In the LCV Catalog it is measured in deg, and in Hecate it is mesaured in kpc**

@@

```{python}
#| echo: false
logKLum_corr = round(compare_data(dt["logKLum"], dt["logL_K"])[3], 3)
```
|   LCV   | HECATE | Description | Pearson Correlation \[-1,1\] |
|:-------:|:------:|:-----------:|:----------------------------:|
| logKLum | logL_K |             |      `{python} logKLum_corr` |

```{python}
scatter_plot(dt["logKLum"], dt["logL_K"])
```

@@

|         LCV         | HECATE | Description |
|:-------------------:|:------:|:-----------:|
| mag_B (with errors) |  BT (with errors)      |             |
|       Kmag   |     K   | 2MASS band magnitude  (both)          |
|                     |        |             |
## Absorbsion

```{python}
#| echo: false
ab_corr = round(compare_data(dt["AB"], dt["AG"])[3], 3)
#ab_int_corr = round(compare_data(dt["AB_int"], dt["AI"])[3], 3)
```
|  LCV   | HECATE |                  Description                   | Pearson Correlation \[-1,1\] |
|:------:|:------:|:----------------------------------------------:|:----------------------------:|
|   AB   |   AG   |    Galactic extinction/absorption in B band    |      `{python} ab_corr`      |
| AB_int |   AI   | Internal/Intrisic B band extinction/absorption |   0   |
```{python}
scatter_plot(dt["AB"], dt["AG"])#, scatter_plot(dt["AB_int"], dt["AI"])
```
## SFR
